\chapter{Bibliografia}
[1] Road Safety in the European Union. ''Trends, Statistics and Main Challenges''; European Commission, Mobility and Transport DG: Brussels, Belgium, 2015.

[2] Road Safety Vademecum. ''Road Safety Trends, Statistics and Challenges in the EU 2010–2013''; European Commission: Brussels, Belgium, 2014.

[3] CAR 2 CAR Communications Consortium. ''Roadmap between Automotive Industry and Infrastructure Organizations on Initial Deployment of Cooperative ITS in Europe''; CAR 2 CAR Communications Consortium: Braunschweig, Germany, 2012.

[4] Amsterdam Group. ''Cooperative ITS Corridor Joint Deployment''; Amsterdam Group: Amsterdam, The Netherlands, 2013.

[5] ETSI (2009-06). ''Intelligent Transport Systems (ITS) and Vehicular communications and Basic set of applications and Definitions''; ETSI TR 102 638 V1.1.1; European Telecommunications Standards Institute: Sophia Antipolis Cedex, France, 2009.
Sensors 2015, 15 18505

[6] Takahashi, T.; Hyung, K.K.; Kamijo, S. ''Urban road user classification framework using local feature descriptors and HMM''. In Proceedings of the 15th International IEEE Conference on Intelligent Transportation Systems (ITSC), Las Palmas de Gran Canaria, Spain, 16–19 September 2012; pp. 67–72.

[7] Fardi, B.; Neubert, U.; Giesecke, N.; Lietz, H.; Wanielik, G. ''A fusion concept of video and communication data for VRU recognition''. In Proceedings of the 11th International Conference on Information Fusion, Cologne, Germany, 30 June–3 July 2008; pp. 1–8.

[8] Heuel, S.; Rohling, H. ''Pedestrian classification in automotive radar systems''. In Proceedings of the 13th International Radar Symposium (IRS), Warsaw, Poland, 23–25 May 2012; pp. 39–44.

[9] Schaffer, B.; Kalverkamp, G.; Biebl, E. ''A 5.8 GHz Cooperative Transponder System for Localization and Communication in Traffic Safety Applications''. In Proceedings of the 78th Vehicular Technology Conference (VTC Fall), Las Vegas, NV, USA, 2–5 September 2013; pp. 1–5.

[10] Anaya, J.J.; Merdrignac, P.; Shagdar, O.; Nashashibi, F.; Naranjo, J.E. ''Vehicle to pedestrian communications for protection of vulnerable road users''. In Proceedings of the IEEE Intelligent Vehicles Symposium, Dearborn, MI, USA, 8–11 June 2014; pp. 1037–1042.

[11] Dhondge, K.; Song, S.; Choi, B.; Park, H. ''WiFiHonk: Smartphone-Based Beacon Stuffed WiFi Car2X-Communication System for Vulnerable Road User Safety''. In Proceedings of the IEEE 79th Vehicular Technology Conference (VTC Spring), Seoul, Korea, 18–21 May 2014; pp. 1–5.

[12] Dozza, M.; Idegren, M.; Andersson, T.; Fernandez, A. ''Platform enabling intelligent safety applications for vulnerable road users''. Intell. Transp. Syst. 2014, 8, 368–376.

[13] Zeeshan, H.M.; Fethi, F. ''LTE and IEEE 802.11p for vehicular networking: A performance evaluation''. EURASIP J. Wirel. Commun. Netw. 2014, doi:10.1186/1687-1499-2014-89.

[14] Henderson, T.R.; Lacage, M.; Riley, G.F.; Dowell, C.; Kopena, J.B. ''Network simulations with the ns-3 simulator''. In Proceedings of the SIGCOMM Demonstration, Seattle, WA, USA, 17–22 August 2008.

[15] Behrisch, M.; Bieker, L.; Erdmann, J.; Krajzewicz, D. ''Sumo-simulation of urban mobility-an overview. In Proceedings of the Third International Conference on Advances in System Simulation'', Barcelona, Spain, 23–29 October 2011; pp. 55–60.

[x] Unai Hernandez-Jayo, Idoia De-la-Iglesia and Jagoba Perez, ''V-Alert: Description and Validation of a Vulnerable Road User Alert System in the Framework of a Smart City'', \emph{Sensors 2015}, 15(8), 18480-18505; doi:10.3390/s150818480

[xx] U. Hernandez-Jayo, J. Perez and I. de-la-Iglesia, ''Poster: Wearable warning system for improving cyclists safety in the scope of Cooperative systems'', \emph{Vehicular Networking Conference (VNC)}, 2015 IEEE, Kyoto, 2015, pp. 153-154.
doi: 10.1109/VNC.2015.7385563

[xxx] I. de-la-Iglesia, U. Hernandez-Jayo and J. Perez, ''CS4VRU: A Centralized Cooperative Safety System for Vulnerable Road Users Using Heterogeneous Networks'', \emph{Vehicular Technology Conference (VTC Fall)}, 2015 IEEE 82nd, Boston, MA, 2015, pp. 1-5. doi: 10.1109/VTCFall.2015.7390882

[xxxx] U. Hernandez-Jayo, J. Perez, I. de-la-Iglesia and R. Carballedo, ''CS4VRU: Remote monitoring and warning system for Vulnerable Road'', \emph{2016 13th International Conference on Remote Engineering and Virtual Instrumentation (REV)}, Madrid, Spain, 2016, pp. 153-158. doi: 10.1109 / REV.2016.7444456